%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Daron Arakelian, modified from Kamil K Wojcicki
\documentclass[margin,line]{resume}
\usepackage[hidelinks]{hyperref}


%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Daron Arakelian}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Personal\\Links}
    \hfill e-mail: \href{mailto://daronarakelian@gmail.com}{daronarakelian@gmail.com} \vspace{0mm}\\\vspace{0mm}%
    \hfill GitHub: \url{https://github.com/darakelian} \vspace{0mm}\\\vspace{-4.5mm}%

    \section{\mysidestyle Skills} 
    C++, C\#, Python, Java, Git, SQL, Bash, CMake, Atlassian Suite, TeamCity, GitLab CI/CD

    \section{\mysidestyle Profession Profile}
    Experienced back-end developer, with a focus on high-performance code, possessing extensive financial technology/markets and DevSecOps experience. While serving a 4-year ROTC committment as an officer in the U.S. Air Force, I resumed working at Susquehanna in a part-time capacity.
  
%__________________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle Professional\\Experience}
    \textbf{Susquehanna}, Philadelphia, PA \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Engineer - Market Data} \hfill \textbf{June 2022 -- Present}\\
    - Develops high-performance real-time market data parsers in C++ for use in manual and automated trading strategies.\vspace{1mm}\\%
    - Maintains Python and C\# implementations of market data parsers enabling ease of use for internal teams and quant researchers.\vspace{1mm}\\%
    - Implements custom SBE code generators outputting C\# to upgrade the firm's SBE parsers; on average, results in 300\% latency improvements.\vspace{1mm}\\%
    - Designs packaging solutions for C++/C\# parser libraries using Conan2 and NuGet to distribute code across the firm.

    \textbf{U.S. Air Force}, Fort George G. Meade (NSA), MD \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Engineer, Captain, TS/SCI cleared} \hfill \textbf{December 2020 -- Present}\\
    - Led software development efforts on an inter-system communications library spanning multiple teams that was vital to a \$XB/yr national defense missions.\vspace{1mm}\\%
    - Bootstrapped a CI/CD pipeline providing code quality/security scans and consistent build efforts; responsible for championing DevSecOps process for a XX+ person team using GitLab CI/CD, k8s, and SonarQube.\vspace{1mm}\\%
    - Developed a custom configuration management library for use across 10+ projects streamlining the process of runtime configuration for developers.\vspace{1mm}\\%
    - Stood up a Java k8s microservice to replace a legacy monorepo improving reliability and scaleability using Docker.\vspace{1mm}\\%
    - Developed custom automated cyber-vulnerability toolchain using ML/AI to bolster cyber research analysts' abilities to perform vital work helping to safeguard multi-billion dollar weapon systems.\vspace{1mm}\\%
    - Served as AI SME for senior leadership, guiding strategic decision making processes to operationalize AI safely and responsibly, and liaising with private sector industry partners to forge new relations.

    \textbf{Susquehanna}, Philadelphia, PA \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Engineer - Options} \hfill \textbf{March 2019 -- December 2020}\\
    - Developed software for real-time monitoring of market data feeds across 15+ co-located trading systems ensuring system integrity and availability.\vspace{1mm}\\%
    - Introduced modern DevOps CI/CD infrastructure, significantly reducing human touch points during deployments, using TeamCity and Octopus Deploy.\vspace{1mm}\\%
    - Implemented historic trend detections reducing false positive/negative rates by over 20\%

    \textsl{Software Engineer - Market Data Client Apps} \hfill \textbf{March 2018 -- March 2019}\\
    - Maintained and implemented new features for enterprise scale .NET software used to display real-time market data across 800+ trader desktops.\vspace{1mm}\\%
    - Modernized team's CI/CD systems which lead to 20\%+ build time improvements\vspace{1mm}\\%
    - Led development of new full-stack C\# system for market data display access controls ensuring compliance with stock exchange policies.
 
%__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    \textsl{B.S. in Computer Engineering}, Drexel University \hfill \textbf{ September 2015 -- June 2020}\\\vspace{-1mm}%
    \textsl{Phantom Fellowship}, DAF-MIT AI Accelerator \hfill \textbf{ November 2022 -- April 2023 }\\\vspace{-2mm}%


%__________________________________________________________________________________________________________________
    % Honors and Awards
    %\section{\mysidestyle Awards}
    %Joint Achievement Medal, U.S. Air Force, 2024

%__________________________________________________________________________________________________________________
    % Interests
%    \section{\mysidestyle Interests} 


%computer science education, artificial intelligence, machine learning, computer graphics

%______________________________________________________________________________________________________________________

\end{resume}
\end{document}

%______________________________________________________________________________________________________________________
% EOF
